---
title: "STAT/MATH 495: Problem Set 07"
author: "Jeff Lancaster"
date: "2017-10-24"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE, warning = FALSE
  )
set.seed(50)

# Load packages
library(tidyverse)
library(broom)
library(knitr)
library(ROCR)

train <- read_csv("../PS07/data/cs-training.csv") %>% 
  rename(Id = X1)
test <- read_csv("../PS07/data/cs-test.csv") %>% 
  rename(Id = X1)
submission <- read_csv("../PS07/data/sampleEntry.csv")
```

Information on the competition can be found [here](https://www.kaggle.com/c/GiveMeSomeCredit/data).

#Collaboration

Please indicate who you collaborated with on this assignment: None

# Build binary classifier

Build the binary classifier based on a single predictor variable: `DebtRatio`,
`age`, or `MonthlyIncome`. Justify this choice.

```{r}
ggplot(train, aes(as.factor(SeriousDlqin2yrs), age)) + geom_boxplot()
```
I chose Age because the boxplot that my code generates indicates that the average age for people who have had serious delinquincies in the last 2 years is significantly lower than the average age of those who have not.  I guess this makes sense because as you get older, your financial security increases (as a general rule).

```{r,warnings=F}
mod1 <- glm(SeriousDlqin2yrs~age, data=train, family="binomial")
log_odds <- predict(mod1, newdata=test)
p_hat <- 1/(1 + exp(-log_odds))
test<-mutate(test,Probability=p_hat)
submission<-test[,c(1,13)]
write.csv(submission, "submission.csv", row.names = FALSE)
```

# ROC curve

Based on the ultimate classifier you choose, plot a corresponding ROC curve.

```{r}
train2 <- mod1 %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat = 1/(1+exp(-.fitted)))

#ROC curve itself
predicted <- prediction(train2$p_hat, train2$SeriousDlqin2yrs)
rates <- performance(predicted, "tpr","fpr")

#Area under Curve
auc <- as.numeric(performance(predicted,"auc")@y.values)
plot(rates, main=paste("Area under Curve =", round(auc, 3)))
```

# ROC curve for random guessing

Instead of using any predictor information as you did above, switch your
predictions to random guesses and plot the resulting ROC curve.

```{r}
rand_p_hat<-runif(length(train2$SeriousDlqin2yrs),0,1)
pred <- prediction(rand_p_hat, train2$SeriousDlqin2yrs)
perf <- performance(pred, "tpr","fpr")

auc <- as.numeric(performance(pred,"auc")@y.values)
auc #should be close to 0.5, obviously

plot(perf, main=paste("Area Under the Curve =", round(auc, 3))) #should be close to linear with y=x equation
```
